Audio Transport

### 2017-05-16 Paper/paper.tex
Updating notation in the paper. Becoming more complete

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{url}

@@

In order to resolve the vertical incoherence --- the phasing issues within the frame --- my solution like others is to lock regions of the spectrum where phase relations are important. Rather than performing a transport over all bins, bins which are used to represent the same spectral information are lumped together.

@@

\subsection{Phase Accumulation}
Horizontal coherence.
\begin{align*}
  \theta' = \theta + \frac{M}{f_s}\hat{\omega} 
\end{align*}

@@

Combinations of frequencies:
rotating in the same direction
\begin{align}
  X_{01}(\omega) = 
  X_0(\omega)^{1-k}
  X_1(\omega)^k
\end{align}
This maintains that the energy of the signal is constant and that the phase rotates from one state to the other.
However, this rotation can happen in multiple directions:

@@

>>>>

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{url}
\usepackage{algpseudocode}

@@

As we 
In order to resolve the vertical incoherence --- the phasing issues within the frame --- my solution like others is to lock regions of the spectrum where phase relations are important. Rather than performing a transport over all bins, bins which are used to represent the same spectral information are lumped together.

@@

$|S| \leq N$
Segment into how at at most $N$ segments $m$ with arrays $X_m$ 
with center of masses $c_m$ and masses $\rho_m$.
\begin{align}
  \sum_{m\in S} &\rho(m) = 1
\end{align}

@@

After two audio signals have been segmented into $S^0$ and $S^1$
we then compute a transformation matrix
$T:S^0\times S^1\to \mathbb{R}$
that represents the transfer of mass from one segment to the other. 
We want this matrix to minimize the distance the centers of each segment move.
We do not want to transport a negative mass or more mass than is available:
\begin{align}
  0 < T(m^0, m^1) \leq \max(\rho(m^0), \rho(m^1))
\end{align}
Additionally, we want to constrain that all of the mass receives an assignment:
\begin{align}
  \rho(m^0) = &\sum_{m^1\in S^1} T(m^0, m^1)
  \;
  \forall m^0\in S^0
  \\
  \rho(m^1) = &\sum_{m^0\in S^0} T(m^0, m^1)
  \;
  \forall m^1\in S^1
\end{align}
%We want to construct a set of assignments $T$, where each assignment $n\in T$ 
%assigns a mass $\rho_n$ to be transported between segments $m_n^0$ and $m_n^1$.
%\begin{align}
  %0 < \rho_n \leq \max(\rho_{m_n^0}, \rho_{m_n^1})
%\end{align}
%Additionally, we want to constrain that all of the mass receives an assignment:
%\begin{align}
  %\rho_m = &\sum_{\substack{n\in T,\\m_n^0 = m}} \rho_n 
  %\;
  %\forall m\in S^0
  %\\
  %\rho_m = &\sum_{\substack{n\in T,\\m_n^1 = m}} \rho_n 
  %\;
  %\forall m\in S^1
%\end{align}
Given constraints 6, 7, 8 we want to find the assignment $T$ that minimizes the 2-wasserstein distance between the segments.
\begin{align}
  \min_T &\sum_{\substack{m^0\in S^0\\ m^1\in S^1}} T(m^0, m^1)|c(m^0) - c(m^1)|^2
\end{align}
We can satisfy the constrains and approximate the using the following algorithm:

Plot of overlapping pieces

Using this algorithm, we guarantee that the number of assignments is bounded by $|T| \leq 2N - 1$.

\subsection{Phase Accumulation}

When we move a segment of the spectrum to a new pitch, 
the phases within that section rotate either slower or faster.
This change does not make an audible difference within a window itself,
but it can cause interference in the overlap between windows known as \emph{horizontal incoherence}.

Include plot

One solution to this in time-stretching is to estimate the phase of the next frame based on its new instantaneous frequency. 
If a bin with phase $\theta_i^\tau$ is oscillating at exactly $\hat{\omega}_i$, the phase of that bin in the next window $\theta_i^{\tau+1}$ will be
\begin{align*}
  \theta(i, \tau+1) = 
  \theta(i,\tau) + \frac{M}{f_s}\hat{\omega}
\end{align*}
This model is good for , but it breaks down at transients.
Reinitialization steps.

Fortunately however, we have at our disposal the phases of not one but two pitches.
The center of  will oscillate at $(1 - k)\hat{\omega}(m_0) + \hat{\omega}^1_m$.
Therefore we can interpolate.

For every bin $i$ keep track of the accumulated phase $\theta_i^\tau$ which we want to have the following properties:

\begin{align*}
  \Theta_i^\tau &\approx
  \sum_{t = 0}^\tau 
  \frac{R}{f_s}\hat{\omega}_i^t\\
  \Theta_i^\tau &= \theta_i^\tau\pmod{2\pi}
\end{align*}

Therefore we want the synthesis phase of $\theta_i$ at the center of mass of segment $m$ is
\begin{align*}
  \theta_{c_m} = (1-k)\Theta_{c_m^0} + k\Theta_{c_m^1}
\end{align*}

To preserve the vertical coherence between all bins within a singular
we add $\theta_{c_m}' - \theta_{c_m}$ to all pitches
\begin{align*}
  \theta_i' = \theta_i + \theta_{c_m}' - \theta_{c_m}
\end{align*}

This way all the local relationships between phases are kept.

\subsection{Resynthesis}

Once the phases of each segment have been centered around the synthesis phase,
we can synthesize a new spectrum:

\begin{algorithmic}
\\
\For{$n\in\left[0,\frac{M-1}{2}\right]$}
  \State{$Y(n) \leftarrow 0$}
  \Comment{Clear the output}
\EndFor
\\
\For{$m_0\in S_0$, $m_1\in S_1$}
  \\
  \State{$\hat{n} \leftarrow (1 - k)c(m_0) + kc(m_1)$}
  \Comment{$\hat{n}$ is the new COM index}
  \State{$\hat{\Theta} \leftarrow (1 - k)\Theta(c(m_0)) + k\Theta(c(m_1))$}
  \Comment{$\theta'$ is the new COM phase}
  \\
  \For{$n\in U(m_0)$}
    \\
    \State{$n' \leftarrow n + \hat{n} - c(m_0)$}
    \State{$\Theta' \leftarrow \Theta_0(n) + \hat{\Theta} - \Theta_0(c(m_0))$}
    \\
    \State{%
      $Y(n') 
      \leftarrow 
      Y(n') +
      (1 - k)
      \frac{T(m_0, m_1)}{\rho(m_0)}
      |X_0(n)|
      e^{i\theta'}$
    }
    \\
  \EndFor
\EndFor
\end{algorithmic}

reentered by the phase accumulation, 
we can simply linearly interpolate the audio and add it to the spectrum.
Since the

@@

If one of the sources is time varying the source material quickly deteriorates.
Great for constant sounds.
